Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-28 paper_comparison/appendix.Rmd
add caption for n_eval appendix

```{r}
eval_n <- function(n_eval, boot) {
  map_df(1:boot, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = n_eval) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value) %>%
  mutate(n_eval = n_eval)
}

>>>>

```{r n_eval, fig.cap = "Change of power for different number of evalutions on a lineup with uniform fitted value distribution. The power will incrase as the number of evaluations increases, but the margin will decrase."}
eval_n <- function(n_eval, boot) {
  map_df(1:boot, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = n_eval) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value) %>%
  mutate(n_eval = n_eval)
}
